Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-02 docs/_tex/index.tex
low res figures

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Fig1_Map_Drone_Sites.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{Figures/Spectral_shapes_total.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Figure3_workflow.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_Low_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_High_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Boat_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Dike_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGlobal.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{Figures/VIP/Fig_VIP.png}

@@

\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Upscaling/density_vs_Proportion.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Disc_Pigment_Table.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGreen.png}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Compare_reflectance.png}

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Fig1_Map_Drone_Sites.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/Spectral_shapes_total.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Figure3_workflow.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGlobal.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/VIP/Fig_VIP.png}

@@

\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Low_res/Upscaling/density_vs_Proportion.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGreen.png}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}

### 2024-03-02 index.qmd
low res figures

knitr::include_graphics("./Figures/Fig1_Map_Drone_Sites.png")
```

@@

knitr::include_graphics("Figures/Spectral_shapes_total.png")
```

@@

knitr::include_graphics("./Figures/Figure3_workflow.png")

@@

knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_Low_Pred.png")

@@

knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_High_Pred.png")

@@

knitr::include_graphics("./Figures/Maps Pred/FigX-Boat_Pred.png")

@@

knitr::include_graphics("./Figures/Maps Pred/FigX-Dike_Pred.png")
```

@@

knitr::include_graphics("./Figures/Validation/ConfusionMatrixGlobal.png")

@@

knitr::include_graphics("Figures/VIP/Fig_VIP.png")

@@

knitr::include_graphics("Figures/Upscaling/density_vs_Proportion.png")

@@

knitr::include_graphics("./Figures/Disc_Pigment_Table.png")
```

@@

knitr::include_graphics("./Figures/Validation/ConfusionMatrixGreen.png")

@@

knitr::include_graphics("./Figures/Compare_reflectance.png")
```
:::

>>>>

knitr::include_graphics("./Figures/Low_res/Fig1_Map_Drone_Sites.png")
```

@@

knitr::include_graphics("Figures/Low_res/Spectral_shapes_total.png")
```

@@

knitr::include_graphics("./Figures/Low_res/Figure3_workflow.png")

@@

knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png")

@@

knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")

@@

knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png")

@@

knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png")
```

@@

knitr::include_graphics("./Figures/Low_res/Validation/ConfusionMatrixGlobal.png")

@@

knitr::include_graphics("Figures/Low_res/VIP/Fig_VIP.png")

@@

knitr::include_graphics("Figures/Low_res/Upscaling/density_vs_Proportion.png")

@@

knitr::include_graphics("./Figures/Low_res/Disc_Pigment_Table.png")
```

@@

knitr::include_graphics("./Figures/Low_res/Validation/ConfusionMatrixGreen.png")

@@

knitr::include_graphics("./Figures/Low_res/Compare_reflectance.png")
```
:::
